# Minimal R / knitr Example
## Jon Meek - TRU May 2016 - Trenton R Users
## Initialize and plot

In the first R chunk, set "echo=TRUE, message=TRUE, warning=TRUE" to show all work.

```{r initialize, echo=TRUE, message=TRUE, warning=TRUE}
## First R code block, this is a R comment

library(ggplot2)

FigureWidth  <- 16
FigureHeight <- 8

xv <- 0:99
yv <- sin(xv / 5)

ggplot() + geom_line(aes(x = xv, y = yv)) + geom_point(aes(x = xv, y = yv))

```
## The plot in it's own chunk, code and messages supressed

```{r Example1, echo=FALSE, message=FALSE, fig.width = FigureWidth, fig.height = FigureHeight}

ggplot() + geom_line(aes(x = xv, y = yv)) + geom_point(aes(x = xv, y = yv))

```

Generate HTML with a command like:

    Rscript -e "library(knitr); knit2html('minimal-knitr.Rmd')"

this assumes that the user is in the directory containing the code,
and wants the HTML output in the same directory

Or, in a more production friendly way:

    Rscript -e "setwd('/n2/r-reports/'); library(knitr); knit2html('/usr/local/bin/minimal-knitr.Rmd')"

setwd sets the directory where the intermediate .md and final .html
files are written. The argument to knit2html is the path to the
"source code".

RStudio has an interactive GUI way to do the same thing (I believe)
